The problem and promise of scale in multilayer networks

### 2020-01-31 paper/manuscript.Rmd
lcres proper interpret points

>>>>

* decreasing availability of patchy lichen = no edges in these layers, though some small proportion of relocations still exist in those layers
* decreasing connective redundancy because through resolution because lichen decreased in connectivity and landcovers became more homogeneous (?)
* decreasing winter lichen relevance because the degree + number of edges decreased
